---
output:
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pander)
panderOptions('table.alignment.default',
     function(df) ifelse(sapply(df, is.numeric), 'right', 'left'))
```

```{r data, echo=FALSE}
exp_ment <- read.csv("data/experience_mentoring.csv", header = TRUE, sep = ";")
grants <- read.csv("data/grants.csv", header = TRUE, sep = ";")
teach <- read.csv("data/teaching.csv", header = TRUE)
conf <- read.csv("data/conferences_talks.csv", header = TRUE, sep = ";")
outreach <- read.csv("data/outreach.csv", header = TRUE, sep = ";")
service <- read.csv("data/service_consulting.csv", header = TRUE, sep = ";")
library(scholar)
#get_num_distinct_journals("EXdyoWAAAAAJ")
#get_num_top_journals("EXdyoWAAAAAJ")
ib <- get_profile("EXdyoWAAAAAJ")
pubs <- get_publications("EXdyoWAAAAAJ", cstart = 0, pagesize = 100, flush = FALSE)
#str(pubs)
#I may want to retrive ORCIR with rorcid if I update my profile there.
#Publons API can be called too
#Maybe even youtube for visit counts.
offset <- 9 #articles in Gscholar not peer review.
```

Ignasi Bartomeus Roig
======================
```{r , echo = FALSE, results = "asis"}
info <- data.frame(col1 = c("E-mail: nacho.bartomeus@gmail.com",
                            "Date of birth: 09-April-1981",
                            "Nationality: Spanish",
                            "Webpage: [http://www.bartomeuslab.com](http://www.bartomeuslab.com)"),
                   col2 = c("Google Scholar: [http://tinyurl.com/bartomeus](http://tinyurl.com/bartomeus)",
                            "Altmetrics: [https://impactstory.org/u/0000-0001-7893-4389](https://impactstory.org/u/0000-0001-7893-4389)",
                            "R code in Github: [https://github.com/ibartomeus](https://github.com/ibartomeus)",
                            "Twitter: [@ibartomeus](https://twitter.com/ibartomeus)"))
colnames(info) <- NULL
pander::pandoc.table(info, digits = c(50,50), split.table = Inf, split.cells = 100, justify = "left")
```


Short bio:
----------

I am a community ecologist interested in understanding how different drivers of global change are affecting biodiversity and ecosystem functioning. I focus on pollinators and their function: the pollination of 80% of the worldwide plant species. I obtained my PhD (_Suma Cum Laude_) in 2008 at the “Universidad Autónoma de Barcelona", advised by Dr. Montserrat Vilà. My PhD explored how biological plant invasions can modify the structure of plant-pollinator networks (_Oecologia_ 2008, 155:761-770; `r sum(get_article_cite_history("EXdyoWAAAAAJ", "u5HHmVD_uO8C")$cites)` citations). In 2009 I did a short postdoctoral stage with Dr. Daniel Sol (CREAF-CSIC) exploring the role of life history traits on explaining biological invasions (_Science_ 2012, 337:580-583). In 2010 I moved to Dr. Rachael Winfree lab (Rutgers University) with a postdoctoral fellowship funded by the Spanish Education Ministry. I investigated changes in native bee communities over time in North America (_PNAS_ 2013, 110:4656-4660), and changes in bee phenology attributable to climate change (_PNAS_ 2011, 108: 20645–20649). On 2012 I took a postdoctoral position in the Swedish University of Agricultural Sciences with Dr. Riccardo Bommarco to work on the LIBERATION EU FP7-project. I published several collaborative papers showcasing the importance of wild pollinators for crop production. These papers are having a strong impact on how we perceive agro-ecosystems and on EU policy (_Science_ 2013 339:1608-1611, _Nature Comm._ 2015 6:7414, _PNAS_ 2016 113, 146-151). Since 2014 I run my own lab as a "Ramón y Cajal" researcher at Estación Biológica de Doñana (EBD-CSIC), Spain. I published `r get_num_articles("EXdyoWAAAAAJ")-offset` scientific papers cited more than `r ib$total_cites` times (H-index = `r ib$h_index`). I am on the board of the [Spanish Association of Terrestrial Ecology](http://www.aeet.org) (AEET) and in the editorial board of [Journal of Ecology](http://onlinelibrary.wiley.com/journal/10.1111/(ISSN)1365-2745). I am an advanced R user and I believe in the open sharing of data, code and ideas to stimulate science advance. Likewise, I find important to be involved in science outreach in order to transfer my results to the society. I created outreach material for different media and gave public talks in schools and public spaces.   
> All citation sources: Google-Scholar `r Sys.Date()`

Education
---------

* __PhD__ in Ecology (_Suma Cum Laude_), “Integration and impacts of invasive plants on plant-pollination networks”. UAB (Universidad Autónoma de Barcelona). Advisor: M. Vilà. May 2008.

* __MSc__ in Ecology: “The Outcome of Carpobrotus and Opuntia invasions on plant-pollinator Mediterranean networks”. UAB. Advisor: M. Vilà. April 2006.

* __BS__ in Biology, specialization in Vegetal Biology and Ecology. UAB. June 2004.

Scientific experience
----------------------

```{r exp, echo = FALSE, results = "asis"}
#colnames(exp_ment)
exp <- subset(exp_ment, category == "experience", select = c("Period", "Position"))
#colnames(exp) <- NULL
pander::pandoc.table(exp, split.table = Inf, split.cells = 100, justify = "left")
```

Bartomeus lab members
---------------------
```{r phd, echo = FALSE, results = "asis"}
ment <- subset(exp_ment, category == "mentoring", select = c("Period", "position", "Position"))
#can sort by date? need date in readable format :(
colnames(ment) <- c("Period", "Position", "Person")
rownames(ment) <- NULL
pander::pandoc.table(ment, split.table = Inf, split.cells = 100, justify = "left")
```

Publications
------------

I published `r get_num_articles("EXdyoWAAAAAJ")-offset` scientific papers, which were cited more than `r ib$total_cites` times (H-index = `r ib$h_index`). I am among the 10% most cited researchers in the last 5 years in the Ecology/Environment cathegory according to the Essential Science indicators of the Web of Science.

```{r pubs, echo = FALSE, results = "asis"}
#Notes:
#peerJ top10: https://peerj.com/collections/28-agricultural-science-papers-nov-15/
#Add papers in F1000!Gagic, Sol...
#Make sure to highlight mentoring and role of some papers?
#colnames(pubs) <- NULL
pubs <- get_publications("EXdyoWAAAAAJ", cstart = 0, pagesize = 100, flush = FALSE)
#str(pubs)
#head(pubs)
pubs <- pubs[,c(-7, - 8)]
pubs <- pubs[order(pubs$year, decreasing = TRUE),]
#unique(pubs$journal)
pubs_preprints <- subset(pubs, journal %in% c("PeerJ Preprints", "bioRxiv")) 
pubs_non_peerr <- subset(pubs, journal %in% c("", "Quercus", "Invasiones Biológicas, Madrid, CSIC, MCI, Gobierno de España", "Pensoft Publishers", "USDA Technical Bulletin", "Ecosistemas", "Biological Invasions and Animal Behaviour", "Bruker Micro-CT Users Meeting")) 
pubs <- subset(pubs, !journal %in% c("", "Quercus", "Invasiones Biológicas, Madrid, CSIC, MCI, Gobierno de España", "Pensoft Publishers", "USDA Technical Bulletin", "PeerJ Preprints", "bioRxiv", "Ecosistemas", "Biological Invasions and Animal Behaviour", "Bruker Micro-CT Users Meeting"))
levels(pubs$journal)[which(levels(pubs$journal) == "science")] <- "Science"
levels(pubs$journal)[which(levels(pubs$journal) == "F")] <- "F1000 Research"
levels(pubs$journal)[which(levels(pubs$journal) == "Proceedings of the Royal Society B: Biological Sciences")] <- "Proceedings of the Royal Society of London B: Biological Sciences"
pubs$journal <- paste(pubs$journal, pubs$number)
pubs <- pubs[,-4]
pubs <- pubs[,c(1:3,5,4)]
colnames(pubs) <- c("Title", "Authors", "Journal", "Year", "Citations")
rownames(pubs) <- NULL
pander::pandoc.table(pubs, split.table = Inf, split.cells = 100, justify = "left")
#Add in review??
#todo: highlight my name
#Add peerJ and ROC, and Perals already published!
```

**Other publications:**

```{r otherpubs, echo = FALSE, results = "asis"}
pubs_non_peerr$journal <- paste(pubs_non_peerr$journal, pubs_non_peerr$number)
pubs_non_peerr <- pubs_non_peerr[,-4]
pubs_non_peerr <- pubs_non_peerr[,c(1:3,5)]
colnames(pubs_non_peerr) <- c("Title", "Authors", "Published in", "Year")
rownames(pubs_non_peerr) <- NULL
pander::pandoc.table(pubs_non_peerr, split.table = Inf, split.cells = 100, justify = "left")
#Add book chapter!
```

**Publications under review or in preparation**

```{r in_rev, echo = FALSE, results = "asis"}
pubs_preprints$journal <- paste(pubs_preprints$journal, pubs_preprints$number)
pubs_preprints <- pubs_preprints[,-4]
pubs_preprints <- pubs_preprints[,c(1:2,3)]
colnames(pubs_preprints) <- c("Title", "Authors", "Pre-print")
rownames(pubs_preprints) <- NULL
pander::pandoc.table(pubs_preprints, split.table = Inf, split.cells = 100, justify = "left")
#remove peerJ/ROC
#Add Magrach, Sol, Winsa, Magrach, Collado, Stavert  
```

Research Grants
---------------
Since 2013 I got `r sum(grants$Amount, na.rm = TRUE)` EUR in external support, including European, national and private funding.  

**Projects where I am principal investigator (PI) or where I had a main role in writting and executting the project.**

```{r grant, echo = FALSE, results = "asis"}
#make column of funding body
#need to collate number and total amount as PI?
#colnames(grants)
grant_IP <- subset(grants, category %in% c("PI", "Co-PI"),
                   select = c("Period", "Title", "Amount", "Agency"))
#can sort by date? need date in readable format :(
rownames(grant_IP) <- NULL
pander::pandoc.table(grant_IP, split.table = Inf, split.cells = 100, justify = "left")
```

**Projects where I actively participated as researcher**

```{r, echo = FALSE, results = "asis"}
grant_ <- subset(grants, !category %in% c("PI", "Co-PI"),
                   select = c("Period", "Title", "Agency"))
#can sort by date? need date in readable format :(
rownames(grant_) <- NULL
pander::pandoc.table(grant_, split.table = Inf, split.cells = 100, justify = "left")
```

Teaching
--------

```{r teach, echo = FALSE, results = "asis"}
#colnames(teach)
teach <- subset(teach, category == "teaching", select = c("Period", "Place", "Title"))
#colnames(teach) <- NULL
rownames(teach) <- NULL
pander::pandoc.table(teach, split.table = Inf, split.cells = 100, justify = "left")
```

Presentations in conferences
----------------------------

```{r, echo = FALSE}
#colnames(conf)
conf_ <- subset(conf, category == "Presentations_in_congresses", select = c("Period", "Place", "Contribution", "Title"))
```

I participated in `r nrow(conf_)` national and international conferences as main presenter.

```{r conf, echo = FALSE, results = "asis"}
conf_ <- conf_[order(conf_$Period, decreasing = TRUE),]
#can sort by date? need date in readable format :(
#colnames(conf_) <- NULL
rownames(conf_) <- NULL
pander::pandoc.table(conf_, split.table = Inf, split.cells = 100, justify = "left")
```

Service, evaluator & consulting
--------------------------------------

I am commited to contribute to the advance of science by serving in national and international scientific organizations, by offering consulting and transference services to the private sector and co-organizing national scientific meetings and workshops.

```{r eval, echo = FALSE, results = "asis"}
#colnames(service)
eval_ <- subset(service, select = c("Period", "category", "value"))
#can sort by date? need date in readable format :(
eval_ <- eval_[order(eval_$Period, decreasing = TRUE),]
ser <- subset(eval_, category == "other")
eval <- subset(eval_, category == "evaluator")
cons <- subset(eval_, category == "consulting")
```

**Service**

```{r, echo = FALSE, results= "asis"}
colnames(ser)[3] <- "Service"
rownames(ser) <- NULL
pander::pandoc.table(ser[,-2], split.table = Inf, split.cells = 100, justify = "left")
```

**Evaluator**

```{r, echo = FALSE, results= "asis"}
colnames(eval)[3] <- "Organism"
rownames(eval) <- NULL
pander::pandoc.table(eval[,-2], split.table = Inf, split.cells = 100, justify = "left")
```

**Consulting**

```{r, echo = FALSE, results= "asis"}
colnames(cons)[3] <- "Consulting"
rownames(cons) <- NULL
pander::pandoc.table(cons[,-2], split.table = Inf, split.cells = 100, justify = "left")
```

Outreach
--------

I enjoy explaining science to the society and contributing to increase scientific based awareness about important topics, like biodiversity decline.

```{r out, echo = FALSE, results = "asis"}
#colnames(outreach)
out <- subset(outreach, category == "outreach", select = c("Period", "Activity"))
#can sort by date? need date in readable format :(
out <- out[order(out$Period, decreasing = TRUE),]
colnames(out) <- NULL
rownames(out) <- NULL
pander::pandoc.table(out, split.table = Inf, split.cells = 100, justify = "left")
```

Invited Talks
-------------
I have been invited to give talks at five national and international universities. 

```{r talks, echo = FALSE, results = "asis"}
#colnames(conf)
talks <- subset(conf, category == "invited_talks", select = c("Period", "Place", "Title"))
#can sort by date? need date in readable format :(
talks <- talks[order(talks$Period, decreasing = TRUE),]
colnames(talks) <- c("Period", "Country", "Place")
rownames(talks) <- NULL
pander::pandoc.table(talks, split.table = Inf, split.cells = 100, justify = "left")
```

Lab visitors
-------------

Since I run my own lab I had several former collegues and new collaborators visiting for short periods to work in collaborative projects:

```{r vis, echo = FALSE, results = "asis"}
#colnames(exp_ment)
vis <- subset(exp_ment, category == "visits", select = c("Period", "Position"))
vis <- vis[order(vis$Period, decreasing = TRUE),]
#can sort by date? need date in readable format :(
colnames(vis) <- c("Period", "Visitor")
rownames(vis) <- NULL
pander::pandoc.table(vis, split.table = Inf, split.cells = 100, justify = "left")
```

Language skills:
----------------

* First Languages: Spanish and Catalan.  
* English: Proficient reading, speaking, and writting.  
* French: Good reading and basic level of speaking and writing.  
 
Informatic and Programming skills:
---------------------------------

* Advanced level informatics (Macintosh & Windows). Proficiency on a wide array of office automation software.  

* Advanced use of R programming language and statistical packages. Git user [(https://github.com/ibartomeus)](https://github.com/ibartomeus). Contributed to R package `originr` [(http://cran.r-project.org/web/packages/originr/)](http://cran.r-project.org/web/packages/originr/) abd `romdb`. Founder and organizer of the R users meetings of Seville. 

* Experience on modelling (i.e. MaxEnt) and writting simulations in R.   

* Knowledge on html language and data base management (MySQL & PHP).  

* Familiarity with GIS (GRASS, Q-GIS).  

Other achievements and skills:
------------------------------

* Adjunt researcher. University of New England, Australia.

* Volunteer at iwith.org

* President of the excursionist group “CampBase” (2002-2005) and regular practice of trail running, orienteering and alpinism.

* Chess player

* Driving Car Licence

* Parent of two kids.

> Ignasi Bartomeus  
> Sevilla, `r Sys.Date()`

An automatically updated version of the cv can be found at [https://github.com/ibartomeus/CV/blob/master/Bartomeus_CV_exahustive.md](https://github.com/ibartomeus/CV/blob/master/Bartomeus_CV_exahustive.md)